A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-11 paper/ms.tex
add metadata table writer

\begin{abstract}
  The Gaia satellite is revitalizing our understanding of nearby
  open clusters and moving groups.  Here, we focus on the
  underappreciated \cn.  Based on rotation periods from TESS and lithium
  measurements from ground-based spectrographs, we find the age of the
  cluster to be $30\pm XX$\,Myr.  \sn\ is a binary system in the
  cluster, serendipitously observed by the Kepler satellite because
  the primary is nearby and Sun-like.  Kepler\,1627A was found to host
  a $3.7\pm X.X\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  We
  re-validate the existence of \pn, and cement it as the youngest
  planet with a well-measured age observed by the main Kepler mission.
  Newly derived ages from Gaia offer the opportunity to significantly
  expand the census of age-dated planets.  The properties of \pn\ are
  may also help clarify how the orbits and atmospheres of the
  mini-Neptune planets evolve.
\end{abstract}

@@

% \input{maintable_header.tex}
% \input{TOI837_phot_table.tex}
% \input{TOI837_rv_table.tex}
% \input{ic2602_ages.tex}
% \input{starparams.tex}
% \input{compparams.tex}
% \input{model_posterior_table.tex}

@@

\appendix
\section{first appendix}
\label{app:first}

>>>>

\begin{abstract}
  The Gaia satellite is revitalizing our understanding of nearby
  open clusters and moving groups.  Here, we focus on the
  underappreciated \cn.  Based on rotation periods from TESS and
  lithium measurements from ground-based spectrographs, we find the
  age of the cluster to be $30\pm XX$\,Myr.  \sn\ is a binary system
  in the cluster, serendipitously observed by the Kepler satellite
  because the primary is nearby and Sun-like.  Kepler\,1627A was
  previously found to host a $3.7\pm X.X\,R_\oplus$ mini-Neptune on a
  7.2\,day orbit.  We re-validate the existence of \pn, and cement it
  as the youngest planet with a well-measured age observed by the main
  Kepler mission.  Newly derived ages from Gaia offer the opportunity
  to significantly expand the census of age-dated planets -- we offer
  a literature compilation of young stars to enable this expansion.
  The properties of \pn\ are may also help clarify how the orbits and
  atmospheres of the mini-Neptune planets evolve.
\end{abstract}

@@

% \input{TOI837_phot_table.tex}
% \input{TOI837_rv_table.tex}
% \input{ic2602_ages.tex}
% \input{starparams.tex}
% \input{compparams.tex}
% \input{model_posterior_table.tex}

@@

\appendix
\section{Young, Age-Dated, and Age-Dateable Star Compilation}
\label{app:targetlist}

\input{table1.tex}

The \texttt{v0.5} CDIPS target catalog includes some important updates
from previous versions.  As in \citet{bouma_cdipsI_2019}, we collected
membership information for young, age-dated, or age-dateable stars
from across the literature.  Table~\ref{tab:metadata} gives a list of
the sources included, and some brief summary statistics.

The first major important change is that the extent of analyses
performed on the Gaia data at the time of our compilation was wide and
deep enough that we opted to neglect pre-Gaia analyses, except in
cases for which spectroscopically confirmed samples of stars had been
collected.  The membership lists for instance of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014} (MWSC and
DAML) were no longer required, especially given their relatively high
field-star contamination rates compared to Gaia-derived membership
catalogs.

For any of the catalogs for which Gaia DR2 identifiers were not
immediately available, we either followed the spatial (plus
proper-motion) crossmatching procedures described in
\citet{bouma_cdipsI_2019}, or else we pulled the Gaia DR2 source
identifiers associated with the catalog from SIMBAD.  We consequently
opted to drop the $\texttt{ext\_catalog\_name}$ and $\texttt{dist}$
columns maintained in \citet{bouma_cdipsI_2019}, as these were only
populated for a small number of stars.

The most crucial parameters of a given star for our purposes are the
Gaia DR2 source identifier ($\texttt{source\_id}$), the cluster name
($\texttt{cluster}$), and the ($\texttt{age}$).  Given the
hierarchical nature of many stellar associations, we do not attempt to
resolve the cluster names to a single unique string.  The Orion
complex for instance, can be divided into almost one hundred kinematic
subgroups \citep{kounkel_apogee2_2018}.  Similar complexity applies to
the problem of determining homogeneous ages, which we do not attempt
to resolve.  Instead, we simply merged the cluster names and ages
reported by various authors together.

This means that our ``age'' column can be null, for cases in which the
original authors did not report an age, and a reference literature age
was not readily available.  Nonetheless, since we do generally prefer
stars with known ages, we made a few additional efforts to populate
this column.  When available, the age provenance is from the original
analysis of the cluster.  However, in a few cases we adopted other
ages when the string-based crossmatches on the ``cluster'' name was
straightforward.  In particular, we used the ages determined by
\citet{CantatGaudin2020b} to assign ages to the catalogs from
\citet{GaiaCollaboration2018}, \citet{CantatGaudin2018a},
\citet{CastroGinard2020}, and \citet{CantatGaudin2020a}.

The catalogs we included for which ages were not immediately available
were those of \citet{CottenSong2016}, \citet{Oh2017},
\citet{Zari2018}, \citet{Gagne2018a},
\citet{Gagne2018b},\citet{Gagne2018c}, and \citet{Ujjwal2020}.  While
in principle the moving group members discussed by
\citet{Gagne2018a,Gagne2018b,Gagne2018c} and \citet{Ujjwal2020} have
easily associated ages, our SIMBAD cross-matching lost the moving
group association from those studies, which should therefore be
recovered tools such as BANYAN
$\Sigma$.\footnote{\url{http://www.exoplanetes.umontreal.ca/banyan/banyansigma.php}}.
We also included the SIMBAD object identifiers $\texttt{TT*}$,
$\texttt{Y*O}, $\texttt{Y*?}, $\texttt{TT?}$, and $\texttt{pMS*}$.
Finally, we also included every star in the NASA Exoplanet Archive
$\texttt{ps}$ table that had a Gaia identifier available
\citep{NASAExoArchive_ps_20210506}.  If the age had finite
uncertainties, we also included it, since stellar ages determined
through the combination of isochrone-fitting and transit-derived
stellar densities typically have higher precision than from isochrones
alone.

The technical manipulations for the merging, cleaning, and joining
were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual crossmatch (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was performed
asychronously on the Gaia archive
website\footnote{\url{https://gea.esac.esa.int/archive/}}.
